Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-01-31 paper/experiments.tex
Paper update

We compared the proposed MACE algorithm with several state-of-the-art parallel Bayesian optimization methods, including the BLCB algorithm\footnote{We implemented this algorithm, as the available open source implementation only takes discrete input}, the local penalization method with EI acquisition function\footnote{Code downloade from https://github.com/SheffieldML/GPyOpt}, the qKG and qEI method\footnote{The code for qKG and qEI is available at https://github.com/wujian16/Cornell-MOE}. The MACE algorithm and the BLCB algorithm are implemented using c++ language.

@@

% \begin{table}[htbp]
%     \small
%     \centering
%     \caption{Summary of the analytical benchmark functions}
%     \label{tab:summaryanalygical}
%     \begin{tabular}
%         \toprule
%         Function     & Dimension    & SearchDomain         \\ 
%         \midrule
%         Branin       & 2            & $[-5, 10]\times[0, 15]$ \\
%         Alpine1      & 5            & $[-10, 10]^5$           \\
%         Hartmann6    & 6            & $[0, 1]^6$              \\
%         Ackley2      & 2            & $[-32, 32]^2$           \\
%         Ackley10     & 10           & $[-32, 32]^10$          \\
%         Rosenbrock2  & 2            & $[-5, 10]^2$            \\
%         Rosenbrock10 & 10           & $[-20, 20]^10$          \\
%         \bottomrule
%     \end{tabular}
% \end{table}

@@

\begin{enumerate}
        \item Branin
        \item Alpine1
        \item Hart6
        \item Rosenbrock-2
        \item Rosenbrock-10
        \item Ackley-2
        \item Ackley-10
\end{enumerate}

@@

>>>>

We compared the proposed MACE algorithm with several state-of-the-art parallel Bayesian optimization methods, including the BLCB algorithm\footnote{Although there are availble open source implementation of BLCB, we implemented this algorithm, as the available open source implementation only takes discrete input}, the local penalization method with EI acquisition function\footnote{Code downloaded from https://github.com/SheffieldML/GPyOpt}, the qKG and qEI method\footnote{The code for qKG and qEI is available at https://github.com/wujian16/Cornell-MOE}. The MACE algorithm and the BLCB algorithm are implemented using c++ language.

@@

@@

For all functions except the two 10D functions, we set the number of initial random sampling to $N_{init} = 20$ and the number of iterations to 45, and set to batch size $B$ to $B = 1$ and $B=4$ respectively,  the total number of function evaluations is $N_{init} + B \times iter$. For the 10D ackley and 10D rosenbrock functions, we set the number of initial sampling to $N_{init} = 100$ and the number of iterations is fixed to 175. The experiments were repeated for ten times to average the random fluctuations. The convergence plot are shown in Figure~\ref{fig:CovPlotBenchmark}.

\begin{table}[htbp]
    \centering
    \caption{Summary of the analytical benchmark functions}
    \label{tab:summaryanalygical}
    \begin{tabular}{llllllll}
        \toprule
        Function            & Dimension        & Search domain    \\ \midrule
         Branin             & 2                & $[-5,  10]\times[0, 15]$ \\
         Alpine1            & 5                & $[-10, 10]^5$           \\
         Hartmann6          & 6                & $[0,   1]^6$              \\
         Ackley2            & 2                & $[-32, 32]^2$           \\
         Rosenbrock2        & 2                & $[-5,  10]^2$            \\
         Ackley10           & 10               & $[-32, 32]^{10}$          \\
         Rosenbrock10       & 10               & $[-20, 20]^{10}$          \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{table*}[htbp]
    \centering
    \caption{Optimization results of the benchmark functions}
    \label{tab:summaryanalygical}
    \begin{tabular}{lllllllllll}
        \toprule
        Function           & MACE-1             & LCB-1             & EI-1            & MACE-4  & BLCB-4  & EI-LP-4 & qKG-4 & qEI-4  \\ \midrule
         Branin            & 0.3979$\pm$1.31e-5 & 0.3980$\pm$1.1e-4 & 0.414$\pm$0.016 &         &         &         &       &        \\
         Alpine1           & 2.66$\pm$1.06      & 5.67$\pm$1.77     & 2.46$\pm$1.56   &         &         &         &       &        \\
         Hartmann6         & -3.26$\pm$0.06     & -3.20$\pm$0.12    & -3.21$\pm$0.15  &         &         &         &       &        \\
         Ackley2           & 1.72$\pm$1.12      & 1.62$\pm$0.926    & 1.01$\pm$0.98   &         &         &         &       &        \\
         Rosenbrock2       & 0.03$\pm$0.05      & 0.03$\pm$0.02     & 13.55$\pm$9.527 &         &         &         &       &        \\
         Ackley10          &                    &                   &                 &         &         &         &       &        \\
         Rosenbrock10      &                    &                   &                 &         &         &         &       &        \\
        \bottomrule
    \end{tabular}
\end{table*}

@@

\FloatBarrier
